The globular cluster system of the Auriga simulations

### 2020-04-10 AurigaGCS.tex
Added Deason+ 2015, Conroy+ 2019 to comment about stellar halo

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
GCs are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity of GC candidates by 
$0.5$ dex with respect to all star particles, but we still find that the GC 
candidates in the Auriga simulations are more metal-rich than the MW and M31 GCSs. 
Although the (old) star particles represent single stellar populations with a mass 
consistent with that of GCs, they are in fact statistical tracers 
of the stellar population of the galaxy as a whole. Therefore only a (small) 
fraction of the star particles may represent plausible formation sites of GCs, 
whereas the majority represents (halo) field stars - the disk component effectively 
falls outside our selection of star particles due to the age cut. It is implausible 
that all halo stars come from disrupted GCs because the total mass in GCSs 
at redshift zero is generally a few orders of magnitude lower than the total 
mass of stellar haloes of galaxies. If stellar haloes solely consist of disrupted
GCs, then the GC disruption rate would have to be considerably higher than expected
from theoretical models. Overall, our set of GC candidates most likely contains
an overabundance of regular stars. It could be that the resulting metallicity
distribution is then biased towards higher values than what is observed for real 
GCs. An alternative explanation could overmixing of metals at early times.

@@

\subsection{Lower age cut in the GC selection function}
\label{sec:age_min}
Our method is sensitive to the definition that we adopt to classify GC candidates
\citep{2010MNRAS.404.1203F}. Therefore we explore how our results change if we 
include all star particles older than 8 Gyr, and if we further lower the age cut 
to 6 Gyr.

>>>>

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
GCs are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity of GC candidates by 
$0.5$ dex with respect to all star particles, but we still find that the GC 
candidates in the Auriga simulations are more metal-rich than the MW and M31 GCSs. 
Although the (old) star particles represent single stellar populations with a mass 
consistent with that of GCs, they are in fact statistical tracers 
of the stellar population of the galaxy as a whole. Therefore only a (small) 
fraction of the star particles may represent plausible formation sites of GCs, 
whereas the majority represents (halo) field stars - the disk component effectively 
falls outside our selection of star particles due to the age cut. It is implausible 
that all halo stars come from disrupted GCs because the total mass in GCSs 
at redshift zero is generally a few orders of magnitude lower than the total 
mass of stellar haloes of galaxies. If stellar haloes solely consist of disrupted
GCs, then the GC disruption rate would have to be considerably higher than expected
from theoretical models. Moreover, disrupted dwarf galaxies are more likely to 
contribute to the build up of the stellar halo than GCs \citep[e.g.][]{2015MNRAS.448L..77D, 
2019ApJ...887..237C}. Overall, our set of GC candidates most likely contains
an overabundance of regular stars. It could be that the resulting metallicity
distribution is then biased towards higher values than what is observed for real 
GCs. An alternative explanation could overmixing of metals at early times.

@@

\subsection{Lower age cut in the GC selection function}
\label{sec:age_min}
Our method is sensitive to the definition that we adopt to classify GC candidates
\citep[e.g.][]{2018RSPSA.47470616F}. Therefore we explore how our results change if we 
include all star particles older than 8 Gyr, and if we further lower the age cut 
to 6 Gyr. The average fraction of GC candidates that we select from the all the
star particles increases to 35\% and 55\% for an age cut of 8 and 6 Gyr, respectively.
